### 2025-12-12 Scripts/Manuscript/manuscript.Rmd
Finalized rewrites for PLOS One version of pre-print.

---
title             : "Measurement Reliability, Construct Validity, and Transparent Reporting in Original and Replication Research"
shorttitle        : "Measurement Reliability, Validity, and Reporting"

@@

abstract: |
  To assess psychological phenomena we need reliable and valid measurement of the construct(s) of interest. Information should therefore be reported alongside the measure to enable the evaluation of reliability and validity. Additionally, to ensure that reliable and valid measures can be reused in future research, the measure should be documented in sufficient detail. Therefore, we investigated the measurement reporting in a sample of 77 measures within 56 Many Labs replications and related original articles (Ebersole et al., 2016, 2020; Klein et al., 2014, 2018). We found that the information relevant for the reuse of a measure was reported in full for around half the replication measures, and only 5.2% of the original studies. We also observed that only around a third of multi-item measures in original studies and 11.4% in replications reported a reliability coefficient, with comparable proportions for reporting any psychometric validity evidence. Besides reporting, we also performed checks of the reliability and construct validity using the openly available Many Labs item response data. We observed that the reliability and construct validity of the measures was rarely stable across contexts. These results corroborate existing findings that measurement reporting in published research lacks transparency, and that this transparency may in certain contexts cover up insufficient reliability and valdity. Finally, we offer suggestions on how to increase measurement reporting transparancy and the use of validated measures.

keywords          : "reliability, construct validity, measurement, reporting, transparent reporting, replications, psychology"
wordcount         : "225"

@@

classoption       : man
output            : papaja::apa6_docx
knit              : worcs::cite_all
---

@@

The challenge with measurement in quantitative psychological research is that unlike height or weight, psychological constructs cannot be directly measured, as they cannot be directly observed. Instead, we use scores from a measure as an indicator for a psychological construct. Yet, it cannot simply be assumed that any measure will form a good indicator of the constructs of interest. The measure has to be validated by establishing the reliability and construct validity of the measure. Following the definition of Crutzen and Peters, “[r]eliability refers to the consistency of scale scores when a construct is assessed multiple times or in multiple ways” [@crutzenScaleQualityAlpha2017b; pp. 244]. In turn, construct validity refers to whether the variance in the measured item scores between participants can be attributed to the variance in the unobserved construct(s) of interest between participants [@cronbachConstructValidityPsychological1955]. In practice, the measure itself is always validated within one or more use cases of a specific measurement procedure and the context in which that measurement took place, such as the sample characteristics, location, and time.

However, psychological measures often lack reliability and construct validity evidence, either because the evidence is not reported, or because the measures are not validated at all [@beckmanHowReliableAre2004; @barryValidityReliabilityReporting2014; @flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020; @flakeConstructValidityValidity2022]. Flake et al @flakeMeasurementSchmeasurementQuestionable2020 dubbed these such practices --- that raise doubts about the validity of a measurement --- “Questionable Measurement Practices” (QMPs), being a term analogous to Questionable Research Practices [QRPs; @simmonsFalsePositivePsychologyUndisclosed2011a; @johnMeasuringPrevalenceQuestionable2012a; @wichertsDegreesFreedomPlanning2016a]. A recent line of research has already shown QMPs to be relatively common in both original and replication psychology studies, damaging the trustworthiness and applicability of psychological research findings [@flakeConstructValidityValidity2022; @husseyAberrantAbundanceCronbachs2023].

The purpose of this study is to assess the measurement reporting practices of item-based measures in a diverse and seminal sample of original and replication studies in psychology. In addition, we will use the available item response data to calculate reliability and construct validity indices. Through the combination of assessing the measurement reporting and the calculated indices, we reflect on the apparent validity of the measurement based on the reported information, compared to the validity assessment when going beyond the reported information and checking the item response data.

@@

One issue that has been observed with respect to measurement validation is that the reported measurement information is typically insufficient for readers to understand, evaluate, and reuse the measurement that was used. Flake et al @flakeConstructValidityValidity2022 documented the measurement reporting practices among 100 original psychology articles and their respective replications from the Reproducibility Project Psychology [@opensciencecollaborationEstimatingReproducibilityPsychological2015]. They coded the number of measures, the content of the measures, and information describing and justifying the measurement. They observed limited reporting of evidence demonstrating the reliability and validity of the measurement. Additionally, only eight of the 40 translated scales contained validity evidence for the translated version. A similar lack of reliability and validity reporting has been observed in other studies as well [@hoganEmpiricalStudyReporting2004; @flakeConstructValidationSocial2017]. If readers cannot infer the construct validity and reliability of a measure from the reported information, then readers lack the basic information needed to determine whether the measured variables are actually related to the constructs of interest. In turn, if we cannot determine whether the constructs of interest are captured in the measured variables or not, then the relation of the results of the statistical analysis using these variables and any psychological phenomena of interest is also tenuous. In short, if the reported information does not show that the measurement was valid, then any substantive conclusions from the data are left unsupported.

Further findings by Flake et al @flakeConstructValidityValidity2022 and others [@flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020] show that measurement reporting was not only limited in terms of the reliability and validity evidence. A lack of clearly reported information was also observed for basic content descriptions such as the number of items, the response format, and the scoring of the scale. This creates challenges for future researchers who want to reuse the measure to assess the same construct. Specifically, replication studies attempting to reconstruct the measurement from these incomplete descriptions may end up with a measurement that assesses the constructs in a substantially different way from the original study, or even assess different constructs altogether. If different constructs are assessed, the replication cannot be seen as a test of the same phenomenon as in the original study. If the same constructs are assessed, but in a substantially different way, the estimated effects in the replication cannot be easily compared to the effects in the original study. In either case, substantial comparisons between original and replication are hindered.

@@

Two key aspects of measurement quality are reliability and construct validity. Psychometrics offers various methods for assessing these properties [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011]. The results of such psychometric analyses often serve as essential evidence for evaluating a measure’s validity.

Reliability serves as a pre-requisite for a valid measure in most cases, because a measure for which a participant’s response is not consistent, cannot capture a stable construct [Kaplan and Saccuzzo (2013, pp. 154–155)]. It is therefore concerning that --- as mentioned earlier --- the reporting of psychometric indicators of reliability is not common, and is often limited to Cronbach’s Alpha. Unfortunate, because Cronbach’s Alpha comes with strong assumptions that are rarely tested [@crutzenScaleQualityAlpha2017b]. Furthermore, research by Hussey et al @husseyAberrantAbundanceCronbachs2023 has shown evidence that the reporting of reliability may not only be uncommon, but also biased. They observed a disproportional number of Cronbach’s Alpha values at the common acceptably reliability threshold value of .70, and relatively low reporting below .70. Thus, the lack of reported measurement evidence may indicate psychometric skeletons hiding in the closet.

As a result, if we want to evaluate the reliability of a measure in our sample, we cannot rely on the reported information alone to paint us a representative picture. Therefore, we also evaluated the measurement reliability within the Many Labs original and replication studies by estimating it from the item response data. The data on the item responses are openly available per lab for our sample. Therefore, we can evaluate not only the reliability per measure, but also the variation in reliability across labs. The variation is relevant because Cronbach’s Alpha is an indicator of reliability within a particular sample and not of the reliability of the measure in general, as it is proportional to the total variance in the target variable in the sample. Still, many researchers report and interpret Cronbach’s Alpha as a universal quality of the measure [@cortinaWhatCoefficientAlpha1993; @schmittUsesAbusesCoefficient1996]. @maireadshawMeasurementPracticesLargescale2020 have already observed that for Many Labs 2 the overall sample Cronbach’s Alpha level across scales was below .5, a degree of reliability far below what many would consider acceptable for most research purposes. Our second research aim is therefore to extend these findings by empirically evaluating both the degree as well as the variation of reliability of the measures in Many Labs projects 1, 2, 3, and 5.

@@

Besides reliability, construct validity is key to establish for any measure. A multi-stage process is required to statistically and substantially establish a link between the measurement and the construct of interest. For example, the way a measure's items relate to each other and to the underlying concept (the factor relations) can differ substantially across contexts, a concept known as measurement invariance [@hornPracticalTheoreticalGuide1992; @cheungDirectComparisonApproach2012]. Thus, we cannot assume that the measure is valid in each context it is used in or meant to be used in, it is something that has to be established for each context. Besides investigating the factor structure, the measure should also be backed up substantively and logically [@borgstedeMeaningfulMeasurementRequires2023]. However, what we typically observe in psychological research is that measures are rarely substantiated with validity evidence [@beckmanHowReliableAre2004; @barryValidityReliabilityReporting2014; @flakeConstructValidationSocial2017; @flakeConstructValidityValidity2022]. This may in part be because the sample sizes required in validating a scale can often be larger than many studies are able to obtain [@maccallumSampleSizeFactor1999, @gorsuchFactorAnalysis2013]. Alternatively, researchers may not recognize measurement validation as part of their research method. Yet what has also been observed in the literature is that many measures are created ad hoc and reused maybe once or not at all [@weidmanJingleJangleEmotion2017; @elsonPsychologicalMeasuresArent2023; @anvariFragmentedFieldConstruct2025; @anvariDefragmentingPsychology2025]. This makes it extremely unlikely that the validity of these measure will ever be assessed at all, let alone be thoroughly investigated by analyzing measurement invariance across multiple groups using substantial sample sizes [@meadePowerPrecisionConfirmatory2007; @frenchMeasurementInvarianceTechniques2016; @koziolImpactModelParameterization2018].

One preliminary psychometric check that could easily be conducted is to see if the number of constructs measured by the items of the measurement match the intended number of constructs. Most often the scores on a measure or subscales of a measure are aggregated and interpreted as a singular index. In that case, the measure should be unidimensional. Otherwise, the researcher is interpreting a set of scores to be one concept when in fact they are multiple distinct concepts. Additionally, most reliability indicators --- including Cronbach’s Alpha --- cannot properly estimate true variance when it is spread across distinct constructs, and will thus give an inaccurate estimate of reliability [@schmittUsesAbusesCoefficient1996; @crutzenScaleQualityAlpha2017b].

Mairead shaw et al @maireadshawMeasurementPracticesLargescale2020 checked the dimensionality of the measurements from Many Labs 2 [@kleinManyLabs22018b], and while some support for unidimensionality was present, they found that none of the scales in their sample met all of their criteria for unidimensionality. Because the Many Labs replications reused existing measures across contexts, Mairead shaw et al @maireadshawMeasurementPracticesLargescale2020 could assess validity across contexts. Our third research aim is to extend these findings. We will perform our own checks of unidimensionality on measures from Many Labs 1, 2, 3, and 5 per lab, and include a meta-analytic assessment of the variation in unidimensionality across labs. The combined goal of our three research aims is to provide a descriptive account of the reliability, construct validity, and reporting of measurement in the included Many Labs study pairs.

@@

We preregistered data collection, coding protocol, and planned analyses: <https://osf.io/jgxyu>. We deviated from our coding protocol as is explained further in the text. The results from our preregistered analyses are described in [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd). In the main text, we focus on the descriptive results.

@@

## Ethical Approval

This research was approved by the Tilburg University School of Social and Behavioral Sciences Ethical Review Board (nr. TSB_TP_REMA06).

@@

## Data Source
The data consists of three main sources: replication datasets, replication protocols, and original study articles. We retrieved the data of Many Labs 1, 2, 3, & 5 [@kleinInvestigatingVariationReplicability2014a; @ebersoleManyLabs32016; @kleinManyLabs22018b; @ebersoleManyLabs52020d] from their respective OSF pages. Many Labs 4 [@kleinManyLabs42022] was excluded, as there were no publicly available replication protocols. Additionally, we excluded the replication of [@crosbyWhereWeLook2008a] in Many Labs 5, as it made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures.

Our unit of analysis is a measure of a single variable within a replication protocol or original article that was used in the main analysis that was replicated. For example, if conscientiousness and agreeableness were both measured using the Big 5 Personality Test, each of which was a variable in a replicated effect, then both the conscientiousness and agreeableness part of that questionnaire would be coded as their own unit of analysis. We also allowed for multiple variables to be measured per study. We used the replication protocols to identify the measure of each variable. We did not include acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses. Our final sample size was `r nrow(coded_data_replications)` measures of unique variables for both original and replication studies. Initially, the original articles contained 3 more measures of unique variables than the replication protocols. This difference was due to the way that the moral foundations questionnaire was framed in the original article compared to in the replication protocol. In the original article it was framed as measuring five different moral foundations, while in the replication protocol the measure assessed the two overarching categories that were used to test the main effect in both the original and replication research. The measurement information reported was comparable across all five categories, and thus it was deemed that the measurement could be reduced to reflect two overarching categories to facilitate easier comparison between measurement in original and replication.

## Data Collection

The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. We skimmed both the replication protocols and replication datasets to ensure that they were the correct files to code measurement reporting information from. However, no coding or analysis of either of them had taken place before the analyses were preregistered. Further details on the search strategy can be found in the [coding protocol information file](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) in the supplementary materials.

@@

### Replication Protocols

The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of the replication of an original study. These were retrieved from the Open Science Framework (OSF) pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd>).

### Original Articles

We identified and retrieved all original study articles using the citations for these articles in each replication protocol.

@@

## Measures

@@

We evaluated the transparency of the measurement reporting practices within the original articles and replication protocols using our preregistered coding protocol containing items assessing twenty three reporting practices. The items were based on Table \@ref(tab:QMPCodingInfoTable) presented in Flake et al @flakeMeasurementSchmeasurementQuestionable2020, listing what measurement information to report. We coded an item as “true” if the relevant measurement information was clearly reported, “false” if it was missing or unclear, and “not applicable” if it was irrelevant for that measure (e.g., reporting factor analysis results for single-item measures). These items thus indicate transparent reporting practices, which can be seen as the opposite of QMPs. We grouped the items into five categories, each representing a different element in measurement reporting. Example items are listed in Table \@ref(tab:QMPCodingInfoTable).

```{r QMPCodingInfoTable, warning = FALSE}
QMP_info_dataframe <- data.frame(Category = c("Definition", "", "", "Operationalisation", "", "", "", "", "Selection/Creation", "", "", "Quantification", "Modification", "", "", "", "", ""),
           'N Items' = c("1", "", "", "5", "", "", "", "", "7", "", "", "4", "6", "", "", "", "", ""),
           'Example Item' = c("A psychological/sociological definition",
            "is given to the name of the measured",
            "variable within the paper.", 
            "The administration format (pen-and-",
            "paper/computer) and environment (in",
            "public/in a lab) are described (Note:",
            "both should be present for this item to be", 
            "rated as “true”).", 
            "The source of the scale is provided",
            "(in case the scale was newly developed",
            "this should be clearly stated).", 
            "The number of items are described.", 
            "Any format changes are mentioned",
            "(paper-and-pencil <–> computer), if no",
            "changes were made to the format, and",
            "this was mentioned then code as No",
            "modification. If it is not clear, then code",
            "as False."))

# making the column names look less robot speak-y.
colnames(QMP_info_dataframe) <- c("Category", "N Items", "Example Item")

# transfer the data to an APA table for printing
apa_table(
  QMP_info_dataframe, align = c("l", "r", "l")
  , caption = "Example items used to code transparent measurement reporting practices across five categories linking to different aspects of measurement"
  , note = "Selection and creation of a measure share a category because the justifications and requirements in selecting a measure are similar to those for creating a new measure."
  , escape = FALSE, placement = "htp", booktabs = TRUE)

Included within the list of measurement reporting information is crucially also the reported reliability coefficient and type of index (Cronbach’s Alpha, test-retest correlation, inter-rater reliability coefficient, etc.) when present. As well as the presence of any psychometric construct validity evidence for the measure, such as the results from a factor analysis.

After the initial coding, we made minor alterations from the preregistered coding protocol for fourteen of the twenty three measurement reporting practice items. These items were changed after familiarizing ourselves with the way measurement was reported, and it became clear that our criteria were too stringent. For example, in the initial protocol, an example item of the measure had to be present within the article or protocol itself, for the measurement practice to be considered clearly reported. In the revised protocol, references to online appendices with example items were also considered sufficient for this item. The analyses, tables, and figures presented in this article are all based on the revised coding protocol. The equivalent measurement reporting descriptives obtained with the initial protocol can be found in [Supplementary Analyses B](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_ratio_table.rmd).

We initially intended to construct an index from the transparent measurement reporting items and perform regression analyses on this index and associated replication outcomes. However, this index could not be validated properly, due to a lack of reported information and because we do not have any theorized outcome that could function as a suitable index for predictive validity. Results based on this index would be misleading to present here in the main article. A more detailed explanation of what was omitted and why, as well as the results from these preregistered analyses can be found in [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd).

@@

Table \@ref(tab:QMPTable) lists the prevalence of different measurement reporting practices in original and replication studies. Specifically, we calculated the proportion of measures that transparently reported on the item compared to the total number of measures to which the item was applicable. A higher proportion indicates more transparent measurement reporting.

>>>>

---
title             : "Measurement Reliability, Construct Validity, and Transparent Reporting in Original and Replication Psychological Research"
shorttitle        : "Measurement Reliability, Validity, and Reporting"

@@

abstract: |
  While published (replication) studies using measures to assess psychological phenomena need to transparently report information on measurement procedures, validity, and reliability to allow verification and use in future (replication) research, earlier results highlighted common poor reporting of psychological measurement. Here, we investigated the measurement reporting in a sample of 77 measures within 56 Many Labs replications and related original articles (14–17) and found that the information relevant for reusing measures was reported in full in around half the replication measures, and only 5.2% in the original studies. We also observed that only around a third of multiple-item measures in original studies and 11.4% in replications reported reliability coefficients, with comparable proportions for reporting any convergent, discrimant, predictive, or factorial validity evidence. We performed checks of the reliability and unidimensionality of multiple-item measures using the openly available Many Labs item response data. We observed that the reliability and unidimensionality of the measures was rarely stable across labs. These results corroborate existing findings that measurement reporting in published research lacks transparency, and that poor measurement reporting often obscure insufficient reliability and validity. We offer suggestions on how to improve measurement reporting practices and increase the use of validated measures.

keywords          : "reliability, construct validity, measurement, reporting, transparency, replication, reproducibility"
wordcount         : "198"

@@

classoption       : man
output            : papaja::apa6_pdf
knit              : worcs::cite_all
---

@@

Because psychological constructs cannot be directly measured, quantitative psychological researchers use scores from psychological measures to study psychological phenomena. Psychological measurement is no easy feat and so measures will not always form good indicators of the constructs they purport to measure. Measures need to be validated and associated with sufficient reliability to deal with systematic and unsystematic measurement errors to attribute observed variation in scores to the variance in the unobserved construct(s) of interest. Psychometrics offers a wide range of tools to assess reliability and to study validity, ranging from classic Cronbach’s Alpha to asses internal consistencies to item response theory and structural equation models allowing for fitting models that explicate the notion that supposed latent variables relate to observed items scores in the expected manner In practice, however, many psychological measures exhibit subpar (or unclear) reliabilities and are typically validated and psychometrically tested only in limited circumstances, samples, and measurement procedures, while it is likely that they do not behave psychometrically well in all relevant samples, locations, and time points [@maassenDireDisregardMeasurement2025].

Moreover, many measures used in psychological research lack reliability and construct validity evidence altogether, either because the evidence is not reported in studies using them, or because the measures are not validated to begin with [@beckmanHowReliableAre2004; @barryValidityReliabilityReporting2014; @flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020; @flakeConstructValidityValidity2022]. Such practices are rightly @flakeMeasurementSchmeasurementQuestionable2020 dubbed  “Questionable Measurement Practices” (QMPs), being a term analogous to Questionable Research Practices (QRPs; [@simmonsFalsePositivePsychologyUndisclosed2011a; @johnMeasuringPrevalenceQuestionable2012a; @wichertsDegreesFreedomPlanning2016a]). A recent line of research has already shown QMPs to be relatively common in both original and replication psychology studies, damaging the trustworthiness and applicability of psychological research findings [@flakeConstructValidityValidity2022; @husseyAberrantAbundanceCronbachs2023].

The purpose of this study is to assess the measurement reporting practices of item-based measures in a diverse and seminal sample of original and replication studies in psychology. In addition, we will use the available item response data to calculate reliability indices for multiple-item measures and perform a series of unidimensionality checks --- as a prerequisite check of construct validity. By assessing the measurement information as reported together with reliability and unidimensionality using the primary data, we reflect on the apparent validity of the measurement based on the reported information, compared to our validity assessment based on the item response data.

@@

One issue that has been observed with respect to measurement validation is that the reported measurement information is typically insufficient for readers to understand, evaluate, and reuse the measurement that was used. Flake et al. @flakeConstructValidityValidity2022 documented the measurement reporting practices among 100 original psychology articles and their respective replications from the Reproducibility Project Psychology [@opensciencecollaborationEstimatingReproducibilityPsychological2015]. They coded the number of measures, the content of the measures, and information describing and justifying the measurement. The reporting of reliability evidence was assessed through whether Cronbach’s Alpha coefficients were reported. For validity evidence, they looked at citations to existing validity evidence from previous studies documenting the scale’s development or use, and results from a factor analysis providing structural evidence for the measure. They observed limited reporting of both reliability and validity evidence. Additionally, only 8 of the 40 translated scales referenced an existing validity study that described evidence for the translated version. A similar lack of reliability and validity reporting has been observed in other studies as well [@hoganEmpiricalStudyReporting2004; @flakeConstructValidationSocial2017]. If the reported information does not reference any of the references to reliability or validity evidence, then readers lack the basic information needed to make an assessment of whether the measured variables relate to the constructs of interest. In turn, if the reported information does not exhibit some minimal level of validity --- through reliability coefficients, an existing validation study, or factor analysis results --- then any substantive conclusions drawn from the data are left unsupported.

Further findings by Flake et al. @flakeConstructValidityValidity2022 and others [@flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020] show that issues in measurement reporting go beyond a lack of reporting reliability and validity evidence. Basic content descriptions such as the number of items, the response format, and the scoring of the scale are not always clearly reported. This creates challenges for future researchers who want to reuse the measure to assess the same construct. Specifically, replication studies attempting to reconstruct the measurement from these incomplete descriptions may end up with a measurement that assesses the constructs in a substantially different way from the original study, or even assess different constructs altogether. If different constructs are assessed, the replication cannot be seen as a test of the same phenomenon as in the original study. If the same constructs are assessed, but in a substantially different way, the estimated effects in the replication cannot be easily compared to the effects in the original study. In either case, substantial comparisons between original and replication are hindered.

@@

Two key aspects of measurement quality are reliability and construct validity. These can be studied using various psychometric tools  [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011]. The results of such psychometric analyses often serve as essential evidence for evaluating a measure’s validity.

Reliability serves as a pre-requisite for a valid measure in most cases, because a measure for which a participant’s response is not consistent, cannot capture a stable construct [@KaplanPsychologicalTestingPrinciples2013; p. 154–5]. It is therefore concerning that the reporting of psychometric indicators of reliability is often substandard  [@beckmanHowReliableAre2004; @barryValidityReliabilityReporting2014; @flakeConstructValidationSocial2017; @flakeConstructValidityValidity2022], Moreover, reliability reporting often limits itself to Cronbach’s Alpha, which comes with strong assumptions that are rarely tested [@crutzenScaleQualityAlpha2017b; @sijtsmaUseMisuseVery2009]. Furthermore, research by Hussey et al. @husseyAberrantAbundanceCronbachs2023 has shown evidence that the reporting of reliability may not only be uncommon, but also biased. They observed a disproportional number of Cronbach’s Alpha values at the common acceptably reliability threshold value of .70, and relatively low reporting below .70. Thus, the lack of reported measurement evidence may indicate psychometric skeletons hiding in the closet.

As a result, the full evaluation of reliabilities is hindered by the possibly biased reporting in our sample of (replication) studies. Therefore, we also computed the measurement reliability within the Many Labs original and replication studies by estimating it from the raw item data. The data on the item responses are openly available per lab for our sample. Therefore, we can evaluate not only the reliability per measure, but also the variation in reliability across labs. The variation is relevant because Cronbach’s Alpha is an indicator of reliability within a particular sample and not of the reliability of the measure in general, as it is proportional to the total variance in the target variable in the sample. Still, many researchers report and interpret Cronbach’s Alpha as a universal quality of the measure [@cortinaWhatCoefficientAlpha1993; @schmittUsesAbusesCoefficient1996]. Mairead Shaw et al. @maireadshawMeasurementPracticesLargescale2020 have already observed that for Many Labs 2 the overall sample Cronbach’s Alpha level across scales was below .5, a degree of reliability far below what many would consider acceptable for most research purposes. Our second research aim is therefore to extend these findings by empirically evaluating both the degree as well as the variation of reliability of the measures in Many Labs projects 1, 2, 3, and 5.

@@

Besides reliability, construct validity is key to establish for any measure. A multi-stage process is required to statistically and substantially establish a link between the measurement and the construct of interest. For example, the way a measure’s items relate to each other and to the underlying concept (the factor relations) can differ substantially across contexts, a concept known as measurement invariance [@hornPracticalTheoreticalGuide1992; @cheungDirectComparisonApproach2012]. Thus, we cannot assume that the measure is valid in each context it is used in or meant to be used in, it is something that has to be established for each context. Besides investigating the factor structure, the measure should also be backed up substantively and logically [@borgstedeMeaningfulMeasurementRequires2023]. However, what we typically observe in psychological research is that measures are rarely substantiated with validity evidence [@beckmanHowReliableAre2004; @barryValidityReliabilityReporting2014; @flakeConstructValidationSocial2017; @flakeConstructValidityValidity2022], and that many measures are made on the fly and reused maybe once or not at all [@weidmanJingleJangleEmotion2017; @elsonPsychologicalMeasuresArent2023; @anvariFragmentedFieldConstruct2025; @anvariDefragmentingPsychology2025]. It is not entirely surprising that most psychological measures are not fully validated, as this requires its own line of research spanning several years, to determine the relation between measure and construct(s), and how this varies across contexts [@meadePowerPrecisionConfirmatory2007; @frenchMeasurementInvarianceTechniques2016; @koziolImpactModelParameterization2018], and over time [@marshlongitudinalstabilitylatent1994], among other aspects.

However, there are prerequisite checks of construct validity that can be conducted by researchers in most scenarios [@gorsuchFactorAnalysis2013]. One such check is to see if the number of constructs measured by the items of the measurement match the intended number of constructs. Often the scores on a measure or subscales of a measure are aggregated and used as a singular index when included as a variable in a statistical model. In that case, the measure should be unidimensional. Otherwise, the researcher is interpreting a set of scores to be one concept when in fact they are multiple distinct concepts. Additionally, most reliability indicators --- including Cronbach’s Alpha --- cannot properly estimate true variance when it is spread across distinct constructs, and will result in an inaccurate estimate of reliability [@schmittUsesAbusesCoefficient1996; @crutzenScaleQualityAlpha2017b]. Thus, unidimensionality checks offer researchers a practical wat to test if the construct validity of their measure is bound to sink or has the potential to swim.

Mairead Shaw et al. @maireadshawMeasurementPracticesLargescale2020 checked the dimensionality of the measurements from Many Labs 2 [@kleinManyLabs22018b] and while some support for unidimensionality was present, they found that none of the scales in their sample met all of their criteria for unidimensionality. Because the Many Labs replications reused existing measures across contexts, Mairead shaw et al @maireadshawMeasurementPracticesLargescale2020 could assess validity across contexts. Our third research aim is to extend these findings. We will perform our own checks of unidimensionality on measures from Many Labs 1, 2, 3, and 5 per lab, and include a meta-analytic assessment of the variation in unidimensionality across labs. The combined goal of our three research aims is to provide a descriptive account of the reliability, unidimensionality, and reporting of measurement in the included Many Labs study pairs.

@@

We preregistered data collection, coding protocol, and planned analyses: <https://osf.io/jgxyu>. We deviated from our coding protocol as is explained further below. The results from our preregistered analyses are described in [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd). In the main text, we focus on the descriptive results.

@@

## Ethics Approval

This research was approved by the Tilburg University School of Social and Behavioral Sciences Ethics Review Board (under TSB_TP_REMA06).

@@

## Data Source
The data consists of three main sources: replication datasets, replication protocols, and original study articles. 
We retrieved the data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 [@kleinInvestigatingVariationReplicability2014a; @ebersoleManyLabs32016; @kleinManyLabs22018b; @ebersoleManyLabs52020d] from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. Many Labs 4 [@kleinManyLabs42022] was excluded, as there were no publicly available replication protocols. Additionally, we excluded the replication of Crosby et al. [@crosbyWhereWeLook2008a] in Many Labs 5, as it made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures. We skimmed both the replication protocols and replication datasets to ensure that they were the correct files to code measurement reporting information from. However, no coding or analysis of either of them had taken place before the analyses were preregistered. Further details on the search strategy can be found in the [coding protocol information file](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) in the supplementary materials.

@@

### Replication Protocols & Original Articles

The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of the replication of an original study. These were retrieved from the Open Science Framework (OSF) pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document). We identified and retrieved all original study articles using the citations for these articles in each replication protocol.

@@

Our unit of analysis is a measure of a single variable within a replication protocol or original article that was used in the main analysis that was replicated. For example, if conscientiousness and agreeableness were both measured using the Big 5 Personality Test, each of which was a variable in a replicated effect, then both the conscientiousness and agreeableness part of that questionnaire would be coded as their own unit of analysis. We also allowed for multiple variables to be measured per study. We used the replication protocols to identify the measure of each variable. We did not include acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses. Our final sample size was `r nrow(coded_data_replications)` measures of unique variables for both original and replication studies. Initially, the original articles contained 3 more measures of unique variables than the replication protocols. This difference was due to the way that the moral foundations questionnaire was framed in the original article [@grahamLiberalsConservativesRely2009] compared to in the replication protocol for Many Labs 2 [@kleinManyLabs22018b]. In the original article it was framed as measuring five different moral foundations, while in the replication protocol the measure assessed the two overarching categories that were used to test the main effect in both the original and replication research. The measurement information reported was comparable across all five categories, and thus it was deemed that the measurement could be reduced to reflect two overarching categories to facilitate easier comparison between measurement in original and replication.

## Coding of Articles and Replications

@@

We evaluated the transparency of the measurement reporting practices within the original articles and replication protocols using our preregistered coding protocol containing 23 reporting practices. The criteria were based on Table 1 presented in Flake et al. @flakeMeasurementSchmeasurementQuestionable2020, listing what measurement information to report. We coded a criterion as “true” if the relevant measurement information was clearly reported, “false” if it was missing or unclear, and “not applicable” if it was irrelevant for that measure (e.g., reporting factor analysis results for single-item measures). These criteria for transparent reporting practices can be seen as contra-indicators of QMPs. We grouped the criteria into five categories (Definition, Operationalisation, Selection/Creation, Quantification, Modification), each representing a different element in measurement reporting. Selection and creation of a measure share a category because the criteria for selecting a measure are similar to those for creating a new measure. Examples of criteria are: "The administration format (pen-and-paper/computer) and environment (in public/in a lab) are described" (Operationalisation); "The number of items are described" (Quantification). The full coding protocol can be found in the [Revised Coding Protocol](../../SupplementaryMaterials/Measurement_Error_Reporting_Revised_Coding_Protocol.pdf) supplementary document.

Included within the list of measurement reporting information is crucially also the reported reliability coefficient and type of index (Cronbach’s Alpha, test-retest correlation, inter-rater reliability coefficient, etc.) when present. As well as the presence of any psychometric convergent, discriminant, predictive or factorial validity evidence for the measure.

After the initial coding, we made minor alterations from the preregistered coding protocol for 14 of the 23 measurement reporting practices. We revised these coded criteria because early results indicated that our original criteria were too stringent. For example, in the initial protocol, an example item of the measure had to be present within the article or protocol itself, for the measurement practice to be considered clearly reported. In the revised protocol, references to online appendices with example items were also considered sufficient for this criterion. The analyses, tables, and figures presented in this article are all based on the revised coding protocol. The equivalent measurement reporting descriptives obtained with the initial protocol can be found in [Supplementary Analyses B](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_ratio_table.rmd).

We initially intended to construct an index from the transparent measurement reporting criteria and perform regression analyses on this index and associated replication outcomes. However, this index could not be validated properly, due to the lack of reported information, including information that could be used to construct a suitable outcome to assess the index' predictive validity. Results based on this index would be misleading to present here in the main article. A more detailed explanation of what was omitted and why, as well as the results from these preregistered analyses can be found in [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd).

@@

We coded `r nrow(coded_data_original)` measures used across the original and replication studies. Table \@ref(tab:QMPTable) lists the prevalence of different transparent measurement reporting practices in original and replication studies. Specifically, we calculated the proportion of measures that transparently reported on the item compared to the total number of measures to which the item was applicable.

```{r QMPTable}
# create informative Measurement Practice Labels 
MPractice <- c("Reliability is reported", "Clear if the measure is newly created or not",    "Exact version of the measure is specified", "Factor analytical results are presented",   "Measured variable is defined", "Measure selection or creation is justified",    "Implemented operationalisation is justified", "Source of the measure is provided",    "Psychometric evidence from the study is given", "Pre-existing psychometric evidence is given",    "Administration format and place are described", "Administration procedure is described",   "Number of items is described", "Number of response options is described", "Recoding of responses is described", "Creation of the index is described", "Text or supplement has example items", "Administration format changes are mentioned",    "Administration format changes are justified", "Translations are mentioned",    "Translated measures are justified", "Change in N items/response options mentioned",    "Change in N items/response options are justified")
